StatiscalAnalysis_ModelFitting

### 2023-03-20 1 Data Cleaning Script/DataCleaningScript.qmd
Pt.2 Model Fitting
Data re-cleaned, re-explored, and fitted to models

@@

```{r}
#filter out 2020 data
d3 <- d2 %>% filter(yr !=2020)
head(d3)
```

@@

```{r}
#save 2021 data only
stork_AMR_2021 <- d3

#save for both years
stork_AMR_clean <- d2
```

>>>>

Standardize main continuous covariates (mean_lui, nsuccess, age)

```{r}
d2$s.nsuccess <- (d2$nsuccess-mean(d2$nsuccess, na.rm = TRUE))/sd(d2$nsuccess, na.rm = TRUE)

#?sd, use na.rm = TRUE to ensure that NAs are removed from calculations
d2$s.lui <- (d2$mean_lui-mean(d2$mean_lui, na.rm = TRUE))/sd(d2$mean_lui, na.rm = TRUE)

d2$s.age <- (d2$age-mean(d2$age, na.rm = TRUE))/sd(d2$age, na.rm = TRUE)

```

Quantitative data is reported in log10. Will transform columns to data with the inverse log10 that would allow a more accurate evaluation of AMR gene burden via formula; x=10^y where x is the new gene burden and y is the original gene burden calculated from published formula.

```{r}
d2$TET..A <- 10^(d2$TET..A)
d2$TET..B <- 10^(d2$TET..B)
d2$TET..Y <- 10^(d2$TET..Y)
d2$TET..K <- 10^(d2$TET..K)
d2$TET..M <- 10^(d2$TET..M)
d2$TET..Q <- 10^(d2$TET..Q)
d2$TET..S <- 10^(d2$TET..S)
d2$TET..W <- 10^(d2$TET..W)
d2$sulI <- 10^(d2$sulI)
d2$sulII <- 10^(d2$sulII)
d2$str <- 10^(d2$str)
d2$aadA <- 10^(d2$aadA)
d2$catI <- 10^(d2$catI)
d2$catII <- 10^(d2$catII)
d2$ermB <- 10^(d2$ermB)
d2$ermF <- 10^(d2$ermF)
d2$qnrB <- 10^(d2$qnrB)
d2$qnrS <- 10^(d2$qnrS)
d2$blaTEM <- 10^(d2$blaTEM)
d2$mecA <- 10^(d2$mecA)
d2$mcr.1 <- 10^(d2$mcr.1)

d3 <- d2 %>%
  mutate(Burden = rowSums(across(c(TET..A, TET..B, TET..Y, TET..K, TET..M, TET..Q, TET..S, TET..W, sulI, sulII, str, aadA, catI, catII, ermB, ermF, qnrB, qnrS, blaTEM, mecA, mcr.1))))

glimpse(d3)
```

@@

```{r}
#filter out 2020 data
d4 <- d3 %>% filter(yr !=2020)
head(d4)
```

@@

```{r}
#save 2021 data only
stork_AMR_2021 <- d4

#save for both years
stork_AMR_clean <- d3
```

### 2023-03-20 3 Analysis Scripts/Data_Exploratory_Analysis.qmd
Pt.2 Model Fitting
Data re-cleaned, re-explored, and fitted to models

```{r, warning=FALSE, message=FALSE}
#load needed packages
library(here) 
library(dplyr)
library(skimr)
library(ggplot2)
```

@@

#### Explore Data

@@

```{r}
table1 <- stork_AMR_2021 %>%
  select(id, age, nsuccess, mean_lui, MDR) %>%
  knitr::kable()
table1
```

Plotting total MDR outcomes from both years.

```{r}
stork_AMR_clean %>%
  ggplot(aes(MDR))+
  geom_histogram()
```
Plot MDR vs age of bird

```{r}
stork_AMR_clean %>%
  ggplot(aes(as.factor(MDR), age))+
  geom_boxplot()
```
Plot MDR vs nest success

```{r}
stork_AMR_clean %>%
  ggplot(aes(as.factor(MDR), nsuccess))+
  geom_boxplot()
```
Plotting mean landfill use index vs nest success

```{r, warning=FALSE, message=FALSE}
stork_AMR_2021 %>%
  ggplot(aes(mean_lui, nsuccess))+
  geom_point()+
  geom_smooth(method = "lm")
```
Plotting mean landfill use index vs nest success, grouped by MDR outcome.

```{r, message=FALSE, warning=FALSE}
stork_AMR_2021%>%
  ggplot(aes(mean_lui, nsuccess, color=as.factor(MDR)))+
  geom_point()+
  geom_smooth(method = "lm")
```
Plotting MDR vs mean landfill use index

@@

There seems to be a slight decrease in the presence of MDR as landfill use index increases. Otherwise, there are not many apparent trends in the data off the bat. This exploration will help us as we move forward into a more robust statistical analysis.

>>>>

```{r, warning=FALSE, message=FALSE}
#load needed packages
library(here) #calling
library(dplyr) #cleaning
library(skimr)
library(ggplot2) #plotting and visualization
library(ggpubr) #ggscatter to visualize correlations
library(naniar)#missing values graphics and plots
library(UpSetR)#missing values graphics and plots
library(corrplot) #evaluate if covariates are correlated
```

@@

#### Quality Control

```{r}
stork_AMR_clean %>%
  as_shadow_upset() %>%
  upset()

gg_miss_fct(x = stork_AMR_clean, fct = yr)
gg_miss_fct(x = stork_AMR_clean, fct = samp)
```
Quite alot of missing values for 2020. Will likely only be able to do summary stats on 2020 because no LUI data was collected that year (COVID-19 limitations)

#### Data subset for 2021

```{r}
stork_AMR_2021 %>%
  as_shadow_upset() %>%
  upset()

gg_miss_fct(x = stork_AMR_2021, fct = yr)
gg_miss_fct(x = stork_AMR_2021, fct = samp)
```

#### Correlation Check of Covariates

```{r}
#define the variables we want to include in the correlation matrix
variables <- stork_AMR_clean[ , c("s.age", "s.lui", "samp", "s.nsuccess")]

#create correlation matrix
cor(variables, use = "complete.obs") #ignore NAs
corrplot(cor(variables, use = "complete.obs"))

Z <- data.frame(s.age = stork_AMR_clean$s.age, 
                s.lui = stork_AMR_clean$s.lui, 
                s.nsuccess = stork_AMR_clean$s.nsuccess,
                samp = stork_AMR_clean$samp)
pairs(Z, panel = panel.smooth, labels = c("age", "mean_lui", "nsuccess", "samp"))

#More than 0.7 usually is unacceptable
#More than 0.5 you need to be careful; NOTHING over 0.5

##BASIC SPEARMAN
cor.test( stork_AMR_clean$s.age, stork_AMR_clean$s.lui,
         method = "spearman")
cor.test( stork_AMR_clean$s.age, stork_AMR_clean$s.nsuccess,
          method = "spearman")
cor.test( stork_AMR_clean$s.age, stork_AMR_clean$samp,
          method = "spearman")
cor.test( stork_AMR_clean$s.nsuccess, stork_AMR_clean$s.lui,
          method = "spearman")
cor.test( stork_AMR_clean$s.nsuccess, stork_AMR_clean$samp,
          method = "spearman")
cor.test( stork_AMR_clean$s.lui, stork_AMR_clean$samp,
          method = "spearman")
cor.test( stork_AMR_clean$Burden, stork_AMR_clean$MDR,
          method = "spearman")
cor.test( stork_AMR_clean$sum, stork_AMR_clean$MDR,
          method = "spearman") #Correlated!

##Visual Plots with: regression line and confidence interval

#Age + LUI
ggscatter(stork_AMR_clean, x = 'age', y = 's.lui',
          add = "reg.line", conf.int = TRUE,    
          add.params = list(fill = "lightgray"),
          ggtheme = theme_minimal()
)+
  stat_cor(method = "spearman", p.accuracy = 0.001, r.accuracy = 0.01,
           label.y = 0.5)

#Nsuccess + LUI
ggscatter(stork_AMR_clean, x = 's.nsuccess', y = 's.lui',
          add = "reg.line", conf.int = TRUE,    
          add.params = list(fill = "lightgray"),
          ggtheme = theme_minimal()
)+
  stat_cor(method = "spearman", p.accuracy = 0.001, r.accuracy = 0.01,
           label.y = 0.6)

#Nsuccess + Age
ggscatter(stork_AMR_clean, x = 's.nsuccess', y = 'age',
          add = "reg.line", conf.int = TRUE,    
          add.params = list(fill = "lightgray"),
          ggtheme = theme_minimal()
)+
  stat_cor(method = "spearman", p.accuracy = 0.001, r.accuracy = 0.01,
           label.y = 20)

#Variables of interest not correlated; they are independent = Move on to analysis
```

#### Data Exploration and visualization

Will explore both 2020 and 2021 data, but will not model with 2020 as no LUI data was collected this year due to COVID-19 restrictions.

@@

```{r}
table1 <- stork_AMR_clean %>%
  select(id, age, nsuccess, mean_lui, Burden, MDR) %>%
  knitr::kable()
table1
```

Plotting total Burden outcomes from both years.

```{r}
stork_AMR_clean %>%
  ggplot(aes(as.factor(yr), Burden))+
  geom_boxplot()
```
Plotting total Burden outcomes across all sampling periods.
```{r}
stork_AMR_clean %>%
  ggplot(aes(as.factor(samp), Burden))+
  geom_boxplot()
```
Total Number of AMR Gene Classes over both years.

```{r}
stork_AMR_clean %>%
  ggplot(aes(as.factor(yr), sum))+
  geom_boxplot()
```

Sample vs Total Number of AMR Gene Classes
```{r}
stork_AMR_clean %>%
  ggplot(aes(as.factor(samp), sum))+
  geom_boxplot()
```

Plot Gene Burden vs age of bird

```{r}
stork_AMR_clean %>%
  ggplot(aes(age, Burden))+
  geom_point()
```

Plot MDR vs age of bird

```{r}
stork_AMR_clean %>%
  ggplot(aes(as.factor(MDR), age))+
  geom_boxplot()
```

Plot Gene Burden vs age of bird

```{r}
stork_AMR_clean %>%
  ggplot(aes(nsuccess, Burden))+
  geom_point()
```

Plot MDR vs nest success

```{r}
stork_AMR_clean %>%
  ggplot(aes(as.factor(MDR), nsuccess))+
  geom_boxplot()
```

Now we will make a table filtering out 2020.

```{r}
table2 <- stork_AMR_2021 %>%
  select(id, age, nsuccess, mean_lui, Burden, MDR) %>%
  knitr::kable()
table2
```

Plotting mean landfill use index vs nest success

```{r, warning=FALSE, message=FALSE}
stork_AMR_2021 %>%
  ggplot(aes(mean_lui, nsuccess))+
  geom_point()+
  geom_smooth(method = "lm")
```

Plotting mean landfill use index vs nest success, grouped by MDR outcome.

```{r, message=FALSE, warning=FALSE}
stork_AMR_2021%>%
  ggplot(aes(mean_lui, nsuccess, color=as.factor(MDR)))+
  geom_point()+
  geom_smooth(method = "lm")
```

Plotting mean landfill use index vs nest success, grouped by MDR outcome.

```{r, message=FALSE, warning=FALSE}
stork_AMR_2021%>%
  ggplot(aes(mean_lui, nsuccess, color=Burden))+
  geom_point()+
  geom_smooth(method = "lm")
```

Plotting MDR vs mean landfill use index

@@

Plotting Burden vs mean landfill use index

```{r, warning=FALSE}
stork_AMR_2021 %>%
  ggplot(aes(mean_lui, Burden))+
  geom_point()+
  geom_smooth(method = "lm")
```

There seems to be a slight decrease in the presence of MDR and increase in the burden of AMR genes as landfill use index increases. Otherwise, there are not many apparent trends in the data off the bat. This exploration will help us as we move forward into a more robust statistical analysis.

### 2023-03-20 3 Analysis Scripts/StatiscalAnalysis_ModelFitting.qmd
Pt.2 Model Fitting
Data re-cleaned, re-explored, and fitted to models

---
title: "StatiscalAnalysis_ModelFitting"
format: html
editor: visual
---
# Ciconia ciconia analysis script

@@

#path to data
data_location <- here::here("2 Clean Data","stork_AMR_clean.rds")

@@

We’ll start with a single factor repeated measures evaluation the  effect of LUI on blaTEM (betalactam) resistence gene burden.
```{r}
data(data, package = "lme4")

data %>% 
  ggplot(aes(x = samp, y = blaTEM)) + 
  geom_point() + 
  geom_line() +
  facet_wrap(~ nes) 
```

Not really what we need... move on

Build models using lmer and glmer
```{r}
lmer_spec <- 
  linear_reg() %>% 
  set_engine("lmer")

@@

lmer_fit_global <- 
  lmer_spec %>% 
  fit(MDR ~ mean_lui + age + samp + nsuccess +(1|nes), data = data)

#Univariate models
lmer_fit_1 <- 
  lmer_spec %>% 
  fit(MDR ~ mean_lui +(1|nes), data = data)

lmer_fit_2 <- 
  lmer_spec %>% 
  fit(MDR ~ age  +(1|nes), data = data)

@@

lmer_fit_4 <- 
  lmer_spec %>% 
  fit(MDR ~ nsuccess +(1|nes), data = data)

lmer_fit_5 <- 
  lmer_spec %>% 
  fit(MDR ~ mean_lui + samp +(1|nes), data = data)

lmer_fit_6 <- 
  lmer_spec %>% 
  fit(MDR ~ mean_lui + nsuccess +(1|nes), data = data)

lmer_fit_7 <- 
  lmer_spec %>% 
  fit(MDR ~ samp + nsuccess +(1|nes), data = data)

lmer_fit_8 <- 
  lmer_spec %>% 
  fit(MDR ~ mean_lui*age + samp + nsuccess +(1|nes), data = data)

lmer_fit_9 <- 
  lmer_spec %>% 
  fit(MDR ~ mean_lui + age*samp + nsuccess +(1|nes), data = data)

lmer_fit_10 <- 
  lmer_spec %>% 
  fit(MDR ~ mean_lui + age + samp*nsuccess +(1|nes), data = data)

@@

```{r}
AIC_table1 <- compare_performance(lmer_fit_null,lmer_fit_global, lmer_fit_1, lmer_fit_2, lmer_fit_3, lmer_fit_4, lmer_fit_5, lmer_fit_6, lmer_fit_7, lmer_fit_8, lmer_fit_9, lmer_fit_10)

@@

plot(compare_performance(lmer_fit_null,lmer_fit_global, lmer_fit_1, lmer_fit_2, lmer_fit_3, lmer_fit_4, lmer_fit_5, lmer_fit_6, lmer_fit_7, lmer_fit_8, lmer_fit_9, lmer_fit_10, rank = TRUE))
```
Summarize and graph best model (lowwest AIC)

```{r}
lmer_fit_global

@@

model1 <- broom::tidy(lmer_fit_global)
print(model1)

@@

MLp <- plot_model(lmer_fit_global,terms = 'mean_lui', type="pred", 
           show.data = TRUE, show.values = TRUE, show.p = TRUE,
           title = "", show.legend = TRUE, line.size=1,
           axis.title = c("Landfill Use Index",'Multi-Drug Resistence'))

MLp
```

Class Diversity (sum) vs All

```{r}
lmer_fit2_null <- #singular
  lmer_spec %>% 
  fit(sum ~ (1|nes), data = data)

lmer_fit2_global <- 
  lmer_spec %>% 
  fit(sum ~ mean_lui + age + samp + nsuccess +(1|nes), data = data)

#Univariate models
lmer_fit2_1 <- 
  lmer_spec %>% 
  fit(sum ~ mean_lui +(1|nes), data = data)

lmer_fit2_2 <- #singular
  lmer_spec %>% 
  fit(sum ~ age  +(1|nes), data = data)

lmer_fit2_3 <- #singular
  lmer_spec %>% 
  fit(sum ~ samp +(1|nes), data = data)

lmer_fit2_4 <- #singular
  lmer_spec %>% 
  fit(sum ~ nsuccess +(1|nes), data = data)

lmer_fit2_5 <- 
  lmer_spec %>% 
  fit(sum ~ mean_lui + samp +(1|nes), data = data)

lmer_fit2_6 <- 
  lmer_spec %>% 
  fit(sum ~ mean_lui + nsuccess +(1|nes), data = data)

lmer_fit2_7 <- #singular
  lmer_spec %>% 
  fit(sum ~ samp + nsuccess +(1|nes), data = data)

lmer_fit2_8 <- 
  lmer_spec %>% 
  fit(sum ~ mean_lui*age + samp + nsuccess +(1|nes), data = data)

lmer_fit2_9 <- 
  lmer_spec %>% 
  fit(sum ~ mean_lui + age*samp + nsuccess +(1|nes), data = data)

lmer_fit2_10 <- 
  lmer_spec %>% 
  fit(sum ~ mean_lui + age + samp*nsuccess +(1|nes), data = data)

@@

```{r}
AIC_table2 <- compare_performance(lmer_fit2_null,lmer_fit2_global, lmer_fit2_1, lmer_fit2_2, lmer_fit2_3, lmer_fit2_4, lmer_fit2_5, lmer_fit2_6, lmer_fit2_7, lmer_fit2_8, lmer_fit2_9, lmer_fit2_10)

@@

plot(compare_performance(lmer_fit2_null,lmer_fit2_global, lmer_fit2_1, lmer_fit2_2, lmer_fit2_3, lmer_fit2_4, lmer_fit2_5, lmer_fit2_6, lmer_fit2_7, lmer_fit2_8, lmer_fit2_9, lmer_fit2_10, rank = TRUE))
```
Summarize and graph best model (lowwest AIC)

```{r}
lmer_fit2_10
# place results from fit into a data frame with the tidy function

model2 <- broom::tidy(lmer_fit2_10)
print(model2)

@@

CLp <- plot_model(lmer_fit2_10,terms = 'mean_lui', type="pred", 
           show.data = TRUE, show.values = TRUE, show.p = TRUE,
           title = "", show.legend = TRUE, line.size=1,
           axis.title = c("Landfill Use Index",'Total Antibiotic Classes with Resistance'))

CLp
```

## Pause... Big issue. Models don't appear to be working well... Have to go back and reclean the data. Covariates should be standarized; values too large between variables! Correlation between variables should be analyzed, plan to use spearman. Will complete 3/17/23

>>>>

---
title: "StatiscalAnalysis_ModelFitting"
format: html
editor: visual
---

# Ciconia ciconia analysis script

@@

#path to data
data_location <- here::here("2 Clean Data","stork_AMR_2021.rds")

@@

We'll start with a single factor repeated measures evaluation the effect of LUI on blaTEM (betalactam) resistence gene burden.

```{r}
data(data, package = "lme4")

data %>% 
  ggplot(aes(x = samp, y = Burden)) + 
  geom_point() + 
  geom_line() +
  facet_wrap(~ nes) 
```

No obvious trends...

Build models using lmer and glmer

```{r}
lmer_spec <- 
  linear_reg() %>% 
  set_engine("lmer")

@@

lmer_fit_global <- 
  lmer_spec %>% 
  fit(MDR ~ s.lui + s.age + samp + s.nsuccess +(1|nes), data = data)

#Univariate models
lmer_fit_1 <- 
  lmer_spec %>% 
  fit(MDR ~ s.lui +(1|nes), data = data)

lmer_fit_2 <- 
  lmer_spec %>% 
  fit(MDR ~ s.age  +(1|nes), data = data)

@@

lmer_fit_4 <- 
  lmer_spec %>% 
  fit(MDR ~ s.nsuccess +(1|nes), data = data)

lmer_fit_5 <- 
  lmer_spec %>% 
  fit(MDR ~ s.lui + samp +(1|nes), data = data)

lmer_fit_6 <- 
  lmer_spec %>% 
  fit(MDR ~ s.lui + s.nsuccess +(1|nes), data = data)

lmer_fit_7 <- 
  lmer_spec %>% 
  fit(MDR ~ samp + s.nsuccess +(1|nes), data = data)

lmer_fit_8 <- 
  lmer_spec %>% 
  fit(MDR ~ s.lui*s.age + samp + s.nsuccess +(1|nes), data = data)

lmer_fit_9 <- 
  lmer_spec %>% 
  fit(MDR ~ s.lui + s.age*samp + s.nsuccess +(1|nes), data = data)

lmer_fit_10 <- 
  lmer_spec %>% 
  fit(MDR ~ s.lui + s.age + samp*s.nsuccess +(1|nes), data = data)

lmer_fit_11 <- 
  lmer_spec %>% 
  fit(MDR ~ s.lui + s.age +(1|nes), data = data)

lmer_fit_12 <- 
  lmer_spec %>% 
  fit(MDR ~ s.lui + s.age +  s.nsuccess +(1|nes), data = data)
```

@@

```{r}
AIC_table1 <- compare_performance(lmer_fit_null,lmer_fit_global, lmer_fit_1, lmer_fit_2, lmer_fit_3, lmer_fit_4, lmer_fit_5, lmer_fit_6, lmer_fit_7, lmer_fit_8, lmer_fit_9, lmer_fit_10, lmer_fit_11, lmer_fit_12)

@@

plot(compare_performance(lmer_fit_null,lmer_fit_global, lmer_fit_1, lmer_fit_2, lmer_fit_3, lmer_fit_4, lmer_fit_5, lmer_fit_6, lmer_fit_7, lmer_fit_8, lmer_fit_9, lmer_fit_10, lmer_fit_11, lmer_fit_12, rank = TRUE))
```

Summarize and graph best model (lowwest AIC)

```{r}
check_model(lmer_fit_11)

@@

model1 <- broom::tidy(lmer_fit_11)
print(model1)

@@

MLp <- plot_model(lmer_fit_11,terms = 's.lui', type="pred", 
           show.data = TRUE, show.values = TRUE, show.p = TRUE,
           title = "", show.legend = TRUE, line.size=1,
           axis.title = c("Landfill Use Index",'Multi-Drug Resistence'))

MLp

ggsave(MLp, file="LUIvsMDR_LME.tiff")
```

AMR Gene Burden vs All

```{r}
lmer_fit2_null <- #singular
  lmer_spec %>% 
  fit(Burden ~ (1|nes), data = data)

lmer_fit2_global <- 
  lmer_spec %>% 
  fit(Burden ~ s.lui + s.age + samp + s.nsuccess +(1|nes), data = data) #overfit

#Univariate models
lmer_fit2_1 <- 
  lmer_spec %>% 
  fit(Burden ~ s.lui +(1|nes), data = data)

lmer_fit2_2 <- 
  lmer_spec %>% 
  fit(Burden ~ s.age  +(1|nes), data = data) #overfit

lmer_fit2_3 <- 
  lmer_spec %>% 
  fit(Burden ~ samp +(1|nes), data = data)

lmer_fit2_4 <- 
  lmer_spec %>% 
  fit(Burden ~ s.nsuccess +(1|nes), data = data)

lmer_fit2_5 <- 
  lmer_spec %>% 
  fit(Burden ~ s.lui + samp +(1|nes), data = data)

lmer_fit2_6 <- 
  lmer_spec %>% 
  fit(Burden ~ s.lui + s.nsuccess +(1|nes), data = data)

lmer_fit2_7 <- 
  lmer_spec %>% 
  fit(Burden ~ samp + s.nsuccess +(1|nes), data = data)

lmer_fit2_8 <- 
  lmer_spec %>% 
  fit(Burden ~ s.lui*s.age + samp + s.nsuccess +(1|nes), data = data) #overfit

lmer_fit2_9 <- 
  lmer_spec %>% 
  fit(Burden ~ s.lui + s.age*samp + s.nsuccess +(1|nes), data = data) #overfit

lmer_fit2_10 <- 
  lmer_spec %>% 
  fit(Burden ~ s.lui + s.age + samp*s.nsuccess +(1|nes), data = data) #overfit

lmer_fit2_11 <- 
  lmer_spec %>% 
  fit(Burden ~ s.lui + s.age + s.nsuccess +(1|nes), data = data) #overfit

lmer_fit2_12 <- 
  lmer_spec %>% 
  fit(Burden ~ s.lui + s.age +(1|nes), data = data) #overfit

#Standardizing variables helped with the overfit/singular model results
```

@@

```{r}
AIC_table2 <- compare_performance(lmer_fit2_null,lmer_fit2_global, lmer_fit2_1, lmer_fit2_2, lmer_fit2_3, lmer_fit2_4, lmer_fit2_5, lmer_fit2_6, lmer_fit2_7, lmer_fit2_8, lmer_fit2_9, lmer_fit2_10, lmer_fit2_11, lmer_fit2_12)

@@

plot(compare_performance(lmer_fit2_null,lmer_fit2_global, lmer_fit2_1, lmer_fit2_2, lmer_fit2_3, lmer_fit2_4, lmer_fit2_5, lmer_fit2_6, lmer_fit2_7, lmer_fit2_8, lmer_fit2_9, lmer_fit2_10, lmer_fit2_11, lmer_fit2_12, rank = TRUE))
```

Summarize and graph best model (lowwest AIC)

```{r}
check_model(lmer_fit2_5)

model2 <- broom::tidy(lmer_fit2_5)
print(model2)

@@

BLp <- plot_model(lmer_fit2_5,terms = 's.lui', type="pred", 
           show.data = TRUE, show.values = TRUE, show.p = TRUE,
           title = "", show.legend = TRUE, line.size=1,
           axis.title = c("Landfill Use Index",'Total Antibiotic Resistant Gene Burden'))

BLp

ggsave(BLp, file="LUIvsBurden_LME.tiff")
```

Preliminary results

Questions: 
Should over fit models be taken out of performance analysis?
What is the best tool/package to control for small data sets?
